\documentclass[nenglish]{AMsemesterArbeit}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{pdflscape}
\usepackage{longtable}
\usepackage{footnote}
\usepackage{import}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{mycommands}
\usepackage{nccmath}
\usepackage{morefloats}
\addbibresource{ABC.bib}


\graphicspath{{Grafiken/GOptimierung/}{Grafiken/GTheorie/}}

\author{Yifei Wang}
\title{%
	Implementation and Investigation of Stress-Recovery-Algorithms in the Finite Element Toolbox AMfe
	%Expand of Finite Element Toolbox
	}
\date{30.\,05.~2016}
\supervisor{Johannes Rutzmoser}

\usepackage[printwatermark]{xwatermark}


\begin{document}
\renewcommand{\arraystretch}{2.5}
\frontmatter
\maketitle
\section*{Abstract}
The motivation of this paper is to implement Python code in Finite Element Toolbox AMfe for the purpose of achieving an relatively exact approximation of strain and stress. The assignment we are trying to complete in this paper is the expansion of Finite Element Toolbox AMfe, which will make it possible to solve strain and stress with 2D element types, namely Tri3, Tri6, Quad4, Quad8 and 3D element types, namely Tet4 and Tet10. The approach we adopted to solve the problem is Stress-Recovery-Algorithms. This is a method based on extrapolation from Gauss points in contrast to the Direct-Evaluation-Algorithms. The objects of my analysis for stress recovery in this research are six element types: quadrilateral element with four nodes (Quad4), quadrilateral element with eight nodes (Quad8), triangular element with three nodes (Tri3), triangular element with six nodes (Tri6), tetrahedral element with four nodes (Tet4), and tetrahedral element with four node (Tet10). Patch test for both algorithms and a convergence analysis for all six element types are also presented in this paper. Towards the end of this paper, the strain and stress contour plot by both algorithms(Stress-Recovery-Algorithm and Direct-Evaluation-Algorithms) will be compared to the solution calculated by the commercial Finite Element software ANSYS. The significance of our obtained results is that the solution of Stress-Recovery-Algorithms is closer to the analytical solution than the solution of Direct-Evaluation-Algorithms for Tri6, Quad4, Quad8, and Tet10. For both element types Tri3 and Quad4, the respective results for nodal stress from the Stress-Recovery-Algorithms and the Direct-Evaluation-Algorithms are exactly the same.


\include{Danksagung}
\PrintTablesAndListsOfContents
\mainmatter
\include{Einleitung}
\backmatter
\AMPrintBibliography
\end{document}

% Compilation process:
%pdflatex Masterarbeit.tex
%biber Masterarbeit
%pdflatex Masterarbeit.tex
%pdflatex Masterarbeit.tex
